% resume.tex
%
% (c) 2002 Matthew Boedicker <mboedick@mboedick.org> (original author) http://mboedick.org
% (c) 2003-2007 David J. Grant <davidgrant-at-gmail.com> http://www.davidgrant.ca
% (c) 2007-2014 Todd C. Miller <Todd.Miller@courtesan.com> http://www.courtesan.com/todd
%
% This work is licensed under the Creative Commons Attribution-ShareAlike 3.0 Unported License. To view a copy of this license, visit http://creativecommons.org/licenses/by-sa/3.0/ or send a letter to Creative Commons, 171 Second Street, Suite 300, San Francisco, California, 94105, USA.
%Modifired: Justin McLennan

\documentclass[letterpaper,11pt]{article}

%-----------------------------------------------------------
\usepackage[empty]{fullpage}
\usepackage{color}
\definecolor{mygrey}{gray}{0.80}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Adjust margins to 0.5in on all sides
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.0in}
\addtolength{\topmargin}{-0.5in}
\addtolength{\textheight}{1.0in}

%-----------------------------------------------------------
%Custom commands
\newcommand{\resitem}[1]{\item #1 \vspace{-2pt}}
\newcommand{\resheading}[1]{{\large \colorbox{mygrey}{\begin{minipage}{\textwidth}{\textbf{#1 \vphantom{p\^{E}}}}\end{minipage}}}}
\newcommand{\ressubheading}[4]{
\begin{tabular*}{7.0in}{l@{\extracolsep{\fill}}r}
		\textbf{#1} & #2 \\
		\textit{#3} & \textit{#4} \\
\end{tabular*}\vspace{-6pt}}
%-----------------------------------------------------------


\begin{document}
\begin{tabular*}{7.5in}{l@{\extracolsep{\fill}}r}
\textbf{\large Justin McLennan}  & 778.229.3503 (cell)\\
3958 Wood Way &  Justin.Mcle@gmail.com \\
Port Coquitlam, BC  V3B 4B4& www.linkedin.com/in/justin-l-mclennan\\
\end{tabular*}
\\

\vspace{0.2in}
\resheading{Skills}

\begin{description}
\item[Languages:]
C/C{}\verb!++!, C\#, Java, Lua, Groovy, SQL, Json, JavaScript, Python
\item[Operating Systems:]
Linux, Windows
\item[Tools:]
Jira, Visual Studio, Unity, Oracle SQL, .NET Framework, Jenkins
\item[Transferable Skills:]
Excellent troubleshooting and debugging ability. Strong leadership, communication and collaboration skills.
\end{description}
\vspace{0.1in}
\resheading{Technical Experience}
\begin{description}
\item    
    \ressubheading{EA Vancouver/Keywords Studio}{FIFA \& NHL 20/21/22}{Associate Software Engineer}{Oct. 2019 - Present}
	\begin{itemize}
	    \item{Maintained and developed automated scripts for projects using C\#.}
	    \item{Collaborated with development and cross-functional teams to troubleshoot and perform root cause analysis.}
	    \item{Assisted with the designing, coding and execution of automated test scripts using Jenkins and Groovy.}
        \item{Maintained documentation of test results to assist in debugging and modification of software.}
        \item{Coordinated with scrum team and development counterparts in overseeing bug tracking, test prioritization, test automation and release.}
        \item{Performed peer code reviews.}
    \end{itemize}
\item    
    \ressubheading{EA Vancouver/Keywords Studio}{NHL 19/20}{Development Support}{Aug. 2018 - Oct. 2019}
	\begin{itemize}
        \item{Created and managed test plans specific to the Hockey Ultimate Team and Live areas.}
        \item{Assessed and progressed Issues flagged through automation.}
        \item{Coordinated with team members daily on regression, smoke testing and checklist completion to verify stability and identify issues.}
        \item{Monitored, escalated and regressed live issues appropriately.}
        \item{Assisted Producers and Developers with designing improvements and game features.}
    \end{itemize}

\item
	\ressubheading{Panoramic Software, Inc.}{Langley, BC}{Software Developer - Practicum}{Apr. 2016 - Aug. 2016}
	\begin{itemize}
    	\item{Created a speech recognition library using the Cortana API.}
		\item{Translated a Universal Windows Platform Calculator Application to a Xamarin Application.}
        \item{Improved and maintained our graphics library.}
	\end{itemize}
\item
	\ressubheading{Project: City Simulator}{British Columbia Institute of Technology}{Server Back-end Team Lead/Git Repo Admin}{Sep. 2017 - Dec. 2017}
	\begin{itemize}
        \item{Built using \emph{.Net Framework} and \emph{Unity} with working \emph{HoloLens} support.}
        \item{Experienced an Agile development cycle with daily scrum meetings.}
        \item{Delegated tasks to appropriate team members, speeding up incident handling.}
        \item{A client-server time based simulation with procedural generated expansion and a basic supply \& demand economy.}
    \end{itemize}
\end{description}
\pagebreak

\begin{tabular*}{7.5in}{l@{\extracolsep{\fill}}r}
\textbf{\large Justin McLennan}  & 778.229.3503 (cell)\\
3958 Wood Way &  Justin.McLe@gmail.com \\
Port Coquitlam, BC  V3B 4B4& https://github.com/J-O-K-E-R\\
\end{tabular*}
\\

\vspace{0.2in}
\resheading{Technical Experience}
\begin{description}
\item
    \ressubheading{Project: Jabber BCIT}{British Columbia Institute of Technology}{Front-End Developer}{Sep. 2016 - Dec. 2016}
	\begin{itemize}
		\item{A social media application for BCIT using a Model-View-Controller architecture.}
        \item{Used \emph{Jquery} to create the front-end of our application.}
        \item{Created using an \emph{Agile} development cycle with daily scrum meetings.}
	\end{itemize}
\end{description}
\resheading{Education}
\begin{description}
\item
	\ressubheading{British Columbia Institute of Technology}{Burnaby, BC}{Associate\textsc{\char13}s Degree (Diploma) Computer Systems Technology}{Sep. 2014 - Dec. 2017}
    \begin{itemize}
    	\item{Designated class representative}
	\end{itemize}
\end{description}
\vspace{0.2in}
\resheading{Non-Technical Work Experience}
\begin{description}
\item
    \ressubheading{The Home Depot}{Port Coquitlam, BC}{Lot Associate/ Order Picker}{Jun. 2014 - Aug. 2018}
	\begin{itemize}
    	\item{Processed, packaged and shipped orders accurately.}
		\item{Handled conflict situations and found solutions to ensure positive interactions with customers.}
        
	\end{itemize}
\item
	\ressubheading{Walmart}{Port Coquitlam, BC}{Store Standards}{Jul. 2012 - Feb. 2014}
	\begin{itemize}
		\item{Maintained a safe clean work environment; Storefront and Parking lot.}
        \item{Provided training and assistance to less experienced employees as required.}
	\end{itemize}

\end{description}

\vspace{0.1in}
\resheading{Interests}
\begin{itemize}
	\item{\textbf{Playing Board Games or D\&D}}
    \item{\textbf{Actively involved in Lacrosse, Ball Hockey and Boxing}}
\end{itemize}

\end{document}
